\documentclass[]{article}

%opening
\title{Meeting Notes for TouchStone}
\author{Ronnie Rodriguez, Joseph Higley, Morgan Something}

\begin{document}

\maketitle

\section{Meeting Notes for Tuesday 9/15/2105}
	\begin{itemize}
		\item Meeting went from 2:30pm - 4:30pm.
	\begin{itemize}
		\item Meeting began by catching Morgan up on what he missed at the team formation meeting the previous Thursday.
		\item Met with the Dean of Engineering to go over exactly what he wants the product to accomplish:
			\begin{itemize}
				\item Must be cutting edge. It needs to really speak to the fact that you are entering the engineering college. It needs to be something that brings people to the building to see, like the Think Tank does.
				\item  Needs to provide a visually appealing, easy to understand interface that users can get important information from, such as campus maps, instructor information, past Deans, etc.
				\item Needs to somehow honor Dean Janssen, the father of the lady who is funding this project. Possibly incorporated into the name?
				\item Needs to be within a budget of roughly 6,000 to 10,000 dollars.
			\end{itemize}
		\item After the Dean left, we brainstormed ideas for the remainder of the time:
			\begin{itemize}
				\item What kind of app?
					\begin{itemize}
						\item Web-based? (HTML, CSS, JS, Python/PHP)
						\item Dedicated App coded in Java or C++?
					\end{itemize}
				\item What technology could we use?
					\begin{itemize}
						\item Projector with touch kiosk?
						\item Virtual Reality?
						\item Projector with Kinect to enable touch features?
					\end{itemize}
			\end{itemize}		
	\end{itemize}
	\end{itemize}

\section{Meeting Notes for Tuesday 9/22/2015}
	\begin{itemize}
		\item Meeting went from 2:30pm-3:30pm
	\end{itemize}
	\begin{itemize}
		\item Meeting began by discussing with Morgan our reservations with having a VR component in the project. 
		\item Morgan demonstrated some of the tech, however, and it was persusive. We decided to run the idea by 
		the dean at our next meeting, and see if he thinks it would be sufficient for what he's looking for. 
	\end{itemize}
	
\section{Meeting Notes for Tuesday 9/29/2015}
	\item 


\end{document}
